plottingScript

### 2023-02-08 analyses/optimizeSupport.Rmd
checkpoint

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 5
  iteration: 30
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_meta<-T
#source_python('src/getSUP.py')
library(reticulate)
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0#10^-7

@@

```{r metaPrep,eval=T}
source_python('src/getMetabricData.py')

metabric<-getMetabric()
colnames(metabric)[ncol(metabric)-1]<-'time'
colnames(metabric)[ncol(metabric)]<-'status'
data<-as.data.frame(model.matrix(~.,metabric)[,-1])
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)
data<-data[,-1]

toDiv<-max(data$time)
data$time<-data$time/toDiv
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"metaTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"metaCV.rds")

@@

klist<-readRDS("metaCV.rds")

###these did not work for complex or support
# lr=c(0.001,0.01)
# drpt=c(0.1,0.25,.5)
# layer1=c(100,200,300)
# layer2=c(25,50,100,200)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","tanh")
# alp=c(0,0.5,1)

@@

klist<-readRDS("metaCV.rds")
test<-readRDS("metaTest.rds")
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 25
  )

@@

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

@@

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))
  #paramTrials<-paramTrials[sample(nrow(paramTrials), 2), ]

@@

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds)
      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
                     ),
                as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))

@@

klist<-readRDS("metaCV.rds")
test<-readRDS("metaTest.rds")

@@

saveRDS(winners,"metaWins.rds")

@@

winners<-readRDS("metaWins.rds")

klist<-readRDS("metaCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

@@

  fullTest<-readRDS("metaTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds)

@@

  train<-normalizer(train,means,sds)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  valcb$offset<-0
  valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 27
  )

@@

  lr=winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=winners$ds$bsize
  actv=winners$ds$actv
  source_python('src/dsurv.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

@@

  #############################
  ###CBNN
  #############################

  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  #bsize=winners$cbnn$bsize
  actv=winners$cbnn$actv

  currentTime<-Sys.time() 
  valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))

@@

  cbnn<-cbnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )
  fit<-fitSmoothHaz(cbnn,
                    epochs=epo,
                    batch_size=c(floor(nrow(mod_cb_glm$data)/100)),
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)

  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100metaBrier.rds')
  saveRDS(cScore,'results/100metacidx.rds')
  pos=pos+1

@@

```{r plotmeta}

BrierIPAList<-readRDS('results/100metaBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.4))
#end_time-start_time

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 5
  iteration: 10
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0# 10^-7

@@

```{r supPrep,eval=T}

source_python('src/getSUP.py')
data<- as.data.frame(do.call(cbind, getSupportPycox()))

colnames(data)[ncol(data)-1]<-'time'
colnames(data)[ncol(data)]<-'status'

#for(i in c(2,5,6,7,16)){#3,4,
#  data[, i]<-as.factor(data[, i])
#}
data<-as.data.frame(model.matrix(~.,data)[,-1])
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))

covs<-colnames(data)
names(data)[ncol(data)-2] <- paste("z", ncol(data)-2, sep="")
names(data)[ncol(data)-1]<-"time"
names(data)[ncol(data)]<-"status"

covs<-colnames(data)
data<-data[,-1]

toDiv<-max(data$time)
data$time<-data$time/toDiv
#data$time<-data$time/max(data$time)
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"supportTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"supportCV.rds")

@@

klist<-readRDS("supportCV.rds")

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 25
  )

@@

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,floor(nrow(train)/100),
                           epochs=epo,valida=val,patience=patience,
                           min_delta=min_delta,drpt=drpt,
                           lay1=layer1,lay2=layer2,
                           lr=lr,actv=actv,alp=alp
                           )

      tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

@@

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds)
     # train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])),
                as.matrix(valcb[,ncol(valcb)-1,drop=F]))

      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")

@@

saveRDS(winners,"supportWins.rds")

@@

winners<-readRDS("supportWins.rds")

klist<-readRDS("supportCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("supportTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds)

@@

  train<-normalizer(train,means,sds)

  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 27
  )

@@

  lr=0.001#winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=winners$ds$bsize
  actv=winners$ds$actv
  source_python('src/dsurv.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

@@

  #############################
  ###CBNN
  #############################
          train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])),
                as.matrix(valcb[,ncol(valcb)-1,drop=F]))

      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  #bsize=winners$cbnn$bsize
  actv=winners$cbnn$actv

  # lr=0.001
  # drpt=0.1
  # layer1=50
  # layer2=20
  # #bsize=winners$cbnn$bsize
  # actv='relu'

  currentTime<-Sys.time() 
  #valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))

@@

        fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=c(floor(nrow(train)/100)),
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

    ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()#+coord_cartesian(ylim=c(-0.1,0.2))
  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100supportBrier.rds')
  saveRDS(cScore,'results/100supportcidx.rds')
  pos=pos+1

@@

```{r plotsupport}

BrierIPAList<-readRDS('results/100supportBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.2))
#end_time-start_time

### 2023-02-08 analyses/plotterScript.Rmd
checkpoint

  allModels<-data.frame(model=c("Null model","Cox_Lin",'CB_Logi','DeepSurv',
                                'DeepHit','PMNN_Spline','PMNN_Poly','Optimal',
                                "dsm"),
                        color=qualitative_hcl(9,palette='Dark 3'),
                        trueName=c("KM","Cox",'CBLR','DeepSurv',
                                'DeepHit','CBNN_Spline','CBNN','Optimal',
                                "DSM"))
  allModels$color[1]="#bfc1c2"
  allModels$color[2]="#FFED11"#"#7C4C74"
  allModels$color[3]= "#80471C" #"#F9A602"
  allModels$color[5]="#FF00AB"
  allModels$color[8]="#000000"
  allModels$color[9]="#8077D5"
 allModels<- allModels[order(allModels$trueName),]
    i <- sapply(metricSummary, is.factor)
    metricSummary[i] <- lapply(metricSummary[i], as.character)
    metricSummary<-metricSummary[complete.cases(metricSummary), ]
    mainTitle<-""
    metricSummary$color<-NA
    for(i in 1:nrow(metricSummary)){
      modelPos<-which(metricSummary$model[i] ==allModels$model)
      metricSummary$model[i]<-allModels$trueName[modelPos]
      metricSummary$color[i]<-allModels$color[modelPos]

@@

```{r plotoldmort,fig.height=6,fig.width=6}

@@

```{r plotgbsg,fig.height=6,fig.width=6}

>>>>

  allModels<-data.frame(model=c("Null model","Cox_Lin",'CB_Logi','DeepSurv',
                                'DeepHit','PMNN_Spline','CBNN_Poly','optimal',
                                "dsm"),
                        color=qualitative_hcl(9,palette='Dark 3'),
                        trueName=c("KM","Cox",'CBLR','DeepSurv',
                                'DeepHit','CBNN_Spline','CBNN','Optimal',
                                "DSM"))
  allModels$color[1]="#bfc1c2"
  allModels$color[2]="#FFED11"#"#7C4C74"
  allModels$color[3]= "#80471C" #"#F9A602"
  allModels$color[5]="#FF00AB"
  allModels$color[8]="#000000"
  allModels$color[9]="#8077D5"
 allModels<- allModels[order(allModels$trueName),]
    i <- sapply(metricSummary, is.factor)
    metricSummary[i] <- lapply(metricSummary[i], as.character)
    metricSummary<-metricSummary[complete.cases(metricSummary), ]
    mainTitle<-""
    metricSummary$color<-NA
    for(i in 1:nrow(metricSummary)){
      modelPos<-which(metricSummary$model[i] ==allModels$model)
      metricSummary$model[i]<-allModels$trueName[modelPos]
      metricSummary$color[i]<-allModels$color[modelPos]

@@

```{r plotoldmort,fig.height=6,fig.width=6,eval=F}

@@

```{r plotgbsg,fig.height=6,fig.width=6,eval=F}
